Distributed Realtime Trajectory Replanning for Robust Motion Execution in Multi-Robot Systems

### 2018-05-11 paper/paper.tex
updated paper

\usepackage{caption}
\usepackage{subcaption}

\captionsetup{compatibility=false}

\usepackage{amsmath}
\usepackage{tikz}
\usepackage{adjustbox}

@@

%flowchart definitions
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
\tikzstyle{decision} = [diamond, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

% vectors in bold
\newcommand{\vp}{\mathbf{p}}
\newcommand{\valpha}{\mathbf{\alpha}}
\newcommand{\vP}{\mathbf{P}}
\newcommand{\vg}{\mathbf{g}}
\newcommand{\vf}{\mathbf{f}}
\newcommand{\vw}{\mathbf{w}}
\newcommand{\vx}{\mathbf{x}}
\newcommand{\vq}{\mathbf{q}}
\newcommand{\vzero}{\mathbf{0}}
\newcommand{\vn}{\mathbf{n}}
\newcommand{\vo}{\mathbf{o}}

% sets as caligraphics
\newcommand{\cV}{\mathcal{V}}
\newcommand{\cS}{\mathcal{S}}

@@

%%%%%%%%%%%%%

@@

We propose robust motion execution as a framework that can take pre-planned trajectories as input and compensate for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and obstacles around them.

Robust motion execution is an extension of cooperative collision avoidance where our objective is to stay close to the originally planned trajectories as much as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.\footnote{test footnote}

% todo: perhaps write some more about what experiments we did, after we have the material

\section{Problem Formulation}
% assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
% input: original curves; positions of peers; dynamic limits; environment (at least able to sense); dt; curve_count; T
% output: at each dt: new trajectory such that there is no collision (guaranteed)
% issues: no live-lock guarantee
We solve our problem completely in a distributed fashion. No central authority coordinates the robots and robots themselves can't communicate with their peers, hence they have no information about the plans of other robots. In every time step $K$, seperated by replanning period $\delta t$, each robot $i$ solves the following problem:
\begin{align*}
    \text{Given,}\ \ \ \ \ &\\
    \vo^i(t')&:\text{ original trajectory of robot $i$},\\
    ct&:\text{ current global time},\\
    \delta t&:\text{ replanning period},\\
    \tau&: \text{time horizon},\\ 
    c&:\text{ maximum continuity between pieces},\\
    \Theta&:\text{ occupancy grid of the environment},\\
    \{\vp_i\}&:\text{ set of positions of all robots},\\
    \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
    &\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
    \text{find a new}&\text{ trajectory $\vf_K^i(t)$ such that},\\
    \vf_K^i(t)&\text{ is}\text{ continuous up to degree $c$ for }t\in [0,\tau],\\
    \frac{d^j\vf_K^i(t)}{dt^j}(0) &= \frac{d^j\vf_{K-1}^i(t)}{dt^j}(\delta t)\text{ for } j\in\{0,1,...,c\}\\
    \vf_K^i(t)&\text{ is collision free for $t\in [0,\delta t]$},\\
    \vf_K^i(t)&\text{ tracks $\vo^i(t')$ as close as possible for $t\in[0,\tau]$ or equivalently $t'\in[ct, ct+\tau]$ }, \text{and}\\
    \left\|\frac{d^j \vf^i(t)}{dt^j}\right\| &\leq \gamma_j\text{ for } t\in [0,\tau],\\
\end{align*}

Robot $i$'s trajectory $f^i(t)$ is $f_K^i(t)$ in $K^{th}$ time step. It follows the trajectory for $\delta t$ seconds, and replans to calculate $f_{K+1}^i(t)$ and replaces $f^i(t)$ with it.

@@

\subsection{Buffered Voronoi Cells}
Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
\begin{align}
    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_i\leq 0 \right\} \label{voronoi_cell_definition}
\end{align}
where $\|\vp\|$ is the L2-norm of vector $\vp$.

The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ that is bounded by hyperplane $H_i^j$ that separates point $\vp_i$ from $\vp_j$ with normal $\valpha_i^j$ and distance along normal $\beta_i^j$ where $\valpha_i^j\in \R^n$ and $\beta_i^j\in \R$ such that
\begin{align*}
    \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\\
    \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i.
\end{align*}

@@

The hyperspace $\cS_i^j$ has the following definition:
\begin{align}
    \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}
\end{align}
Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
\begin{align}
    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j. \label{voronoi_intersection_definition}
\end{align}
This definition suggests a natural algorithm to compute the buffered voronoi cell of any robot $i$ in terms of the hyperplanes $H_i^j$:
\begin{algorithmic}[1]
    \Function{Voronoi}{[$p_i$]: robot positions, $i$: robot that we want to calculate voronoi cell of, $r_i$: radius of robot $i$}
        \State $H = \{\}$
        \ForAll{$j\neq i$}
            \State $H_i^j = (\alpha_i^j, \beta_i^j)$
            \State $H = H\cup H_i^j$
        \EndFor
        \State \Return $H$
    \EndFunction
\end{algorithmic}
This is an $O(m)$ operation, $m$ being the number of robots.

\subsection{B\'ezier Curves}
A degree $d$ b\'ezier curve $\vg(t)$ parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
\begin{align}
    \vg(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T
\end{align}

The curve starts at $\vP_0$ and ends at $\vP_d$. It does not interpolate the control points, but uses them to guide the curve. A b\'ezier curve lies completely inside the convex hull of its control points \cite{Bernstein}. We use this property to give robot-to-robot and robot-to-obstacle no-collision guarantees.

We use polynomial splines as trajectories where each piece is a b\'ezier curve. Given a trajectory $\vf^i(t)$ for robot $i$ with $l$ pieces, $T^i_j$ denotes the duration of $j^{th}$ piece, $\vf^i_j(t; T^i_j)$ denotes the $j^{th}$ piece of the trajectory, $\vP^i_{j,k}$ denotes the $k^{th}$ control point of $j^{th}$ piece, and $P^i_{j,k,u}$ denotes the $u^{th}$ coordinate of that control point where $j \in \{1,2,...,l\}$, $k \in \{0,1,...,d\}$, $u \in \{1,2,...,n\}$.

\subsection{Support Vector Machine}
Support vector machine is a supervised learning method that is used to classify data into several classes. In binary classification problems, given linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label, SVM problem tries to find a hyperplane with normal $\vw$ and distance along the normal $b$ that separates two classes. SVM problem for binary classification with separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
\begin{align*}
    \text{minimize}\ \ \  &\|\vw\|\\
    \text{subject to}\ \ \  & y_i(\vw \cdot \vx_i - b) \geq 1
\end{align*}
We use SVMs to define collision free convex subspaces that are obstacle-free.
\subsection{Trajectory Optimization}
We present our replanning problem as a quadratic optimization problem where the control points of the trajectory are the variables. The overall structure of quadratic optimization problems is as follows \cite{qpOASES}:
\begin{align*}
    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^Tg\\
    \text{subject to}\ \ \ & lbA \leq A\vx \leq ubA\\
    &lb \leq \vx \leq ub
\end{align*}

Each constraint on the problem appends a set of rows to the matrices $A$, $lbA$, and $ubA$. There are 4 types of constraints we impose: starting point constraints, end point constraints, continuity constraints and hyperplane constraints.
\subsubsection{Initial Point Constraints}
For each of the curves in the trajectory, we can impose initial point constraints. An initial point constraint requires curve to have a specific value in any order of its derivatives in the beginning. $S_j(D, T)$ is the matrix we append to $A$ in order to evaluate curve $j$ at its starting point, $D$ being the degree of derivation, $T$ being the duration of the curve.

The value of the curve in the beginning is simply a linear combination of the control points. The rows of $S_j$ are the coefficients of control points in this linear combination, each of which corresponding to a different dimension. We append the desired vector $\vq$ for the constraint to both $lbA$ and $ubA$ matrices. Note that by adding the same vector to both upper and lower bound matrices, we impose an equality constraint.
\subsubsection{End Point Constraints}
This is essentially same with starting point constraints. Only difference is that instead of evaluating the curve at $t=0$, we evaluate it at $t=T$.

$E_j(D,T)$ denotes the matrix we append to $A$ in order to evaluate the curve $j$ at its end point, $D$ being the degree of derivation, $T$ being the duration of the curve. We again append desired value vector $\vq$ to both $lbA$ and $ubA$.
\subsubsection{Continuity Constraints}
For each consecutive curves $j$ and $j+1$ in the trajectory, we can impose a continuity constraint of any degree $D$. We basically take the difference of the $D^{th}$ derivative of curve $j$ evaluated at time $t=T_j$ and the $D^{th}$ derivative of curve $j+1$ evaluated at time $t=0$ and require it to be $\vzero$. This difference is again a linear combination of the control points.

$C_j(D,T_j,T_{j+1})$ denotes the matrix we append to A in order to calculate the difference between curves $j$ and $j+1$, $D$ being the degree of derivation, $T_j$ being the duration of curve $j$ and $T_{j+1}$ being the duration of curve $j+1$. We append $\vzero$ to both $lbA$ and $ubA$.
\subsubsection{Hyperspace Constraints}
For each of the control points, we can add a hyperplane constraint that requires the point not to be in the positive side of the hyperplane. Given hyperplane with normal $\vn$ and distance along the normal $d$, not-positive side of the hyperplane is simply the set $J$ defined as
\begin{align*}
    J = \left\{\vp: \vn \cdot \vp - d \leq 0\right\}
\end{align*}

The constraint is again a linear combination of control points. $H_{j,k}(\vn)$ denotes the row we append to $A$ in order to impose a hyperplane constraint on the $k^{th}$ control point of $j^{th}$ curve, $\vn$ being the normal of the hyperplane. We add $d$ to $ubA$ and $-\infty$ to $lbA$.
\\

Notice that $S_j, E_j, C_j$ and $H_{j,k}$ matrices defined above also depend on the problem dimension $n$ and number of control points per curve $d+1$. To not to complicate the notation, we omitted these details in the symbols. In our treatment, we do not change the number of control points per curve and the dimension of the problem between replanning iterations. Therefore, omitting these details does not present any problems in terms of the completeness of our explanation. In any instance, dimension and points per curve will be inferred from the context.
\section{Approach}

@@

\subsection{Approach Overview}
Our approach has three big components: \emph{discrete planning} that is used in case using only optimization may present problems, \emph{trajectory optimization} to optimize trajectory while avoiding obstacles and other robots, and \emph{dynamic rescaling} to comform to the dynamic limits of the robot.

In each iteration, pipeline that is summarized in figure \ref{fig:flowchart} gets executed. Period of each iteration is $\delta_t$, and all pipeline gets executed every $\delta_t$.

In the beginning of the each iteration, we check for some conditions defined in the following sections to see if we need discrete replanning. If the answer is yes, we do a discrete search that results in a discrete path that is obstacle and robot free. Then, we transform this discrete plan to b\'ezier control points and use those points as the initial data for trajectory optimization. If the answer is no, we skip discrete search, and directly use the control points of the previous plan as the initial data.

Depending on whether we did discrete search or not, we build objective matrix $H$ for trajectory optimization in a slightly different way.

At this point, algorithm has the same flow independent of the fact that we did discrete search or not. We compute $A$ matrix that represents continuity, hyperspace, initial point and end point constraints. Robot-to-robot collision avoidance is enforced with buffered voronoi decomposition of the space while robot-to-obstacle collision avoidance is enforced with SVM hyperspaces that we calculate between trajectory pieces and the obstacles. When the optimization is done, we check whether the dynamic limits are violated. While the answer is yes, we increase durations of pieces and do the optimization again until dynamic limits are not violated. In the end, we have a trajectory $f^i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is $C^{(c)}$ continuous, obeys the dynamic limits of the robot, tries to stay close to the original trajectory and is a good starting point for the next iteration.

\begin{figure}
%\begin{adjustbox}{width=\textwidth,caption={bla}}
\resizebox{\textwidth}{!}{
% \footnotesize
\begin{tikzpicture}[node distance = 2cm]
    \node (discrete) [decision, text width=2cm] {need discrete replanning?};
    \node (discretesearch) [process, right of=discrete, xshift=1.2cm, yshift = 1cm, text width = 2cm] {discrete search};
    \node (discobjbuild) [process, right of=discretesearch, xshift = 1cm, text width = 2cm] {discrete objective builder};
    \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {continuous objective builder};
    \node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
    {constraint builder};
    \node (trajopt) [process, right of=constraintbuild, xshift = 1cm, text width = 2cm] {trajectory optimization};
    \node (dynamiclimits) [decision, right of=trajopt, xshift = 1.5cm, text width = 2cm] {dynamic limits violated?};
    \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {rescaling};
    \node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};

    \coordinate[above=2cm of discrete.west, xshift=-0.2cm] (c1);
    \coordinate[below=2cm of discrete.west, xshift=-0.2cm] (c2);
    \coordinate[above=2cm of discretesearch.east, xshift = 0.2cm, yshift=-1cm] (c3);
    \coordinate[below=2cm of discretesearch.east, xshift = 0.2cm, yshift = -1cm] (c4);

    \coordinate[above=2cm of discobjbuild.west, xshift=-0.2cm, yshift=-1cm] (c5);
    \coordinate[below=2cm of discobjbuild.west, xshift=-0.2cm, yshift = -1cm] (c6);
    \coordinate[above=2cm of trajopt.east, xshift = 0.2cm] (c7);
    \coordinate[below=2cm of trajopt.east, xshift = 0.2cm] (c8);

>>>>

%\usepackage{caption}
%\usepackage{subcaption}
%\captionsetup{compatibility=false}

% Springer does not support subcaption/caption => use subfig instead and avoid loading the caption package
\usepackage[caption=false]{subfig}

\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{adjustbox}

\usepackage{ upgreek }

@@

%flowchart definitions
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=white!30]
\tikzstyle{decision} = [diamond, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=cyan!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

% vectors in bold
\newcommand{\vp}{\mathbf{p}}
\newcommand{\valpha}{\mathbf{\alpha}}
\newcommand{\vP}{\mathbf{P}}
\newcommand{\vg}{\mathbf{g}}
\newcommand{\vf}{\mathbf{f}}
\newcommand{\vw}{\mathbf{w}}
\newcommand{\vx}{\mathbf{x}}
\newcommand{\vq}{\mathbf{q}}
\newcommand{\vzero}{\mathbf{0}}
\newcommand{\vn}{\mathbf{n}}
\newcommand{\vo}{\mathbf{o}}
\newcommand{\vchi}{\mathbf{\chi}}
\newcommand{\vlbA}{\mathbf{lbA}}
\newcommand{\vubA}{\mathbf{ubA}}
\newcommand{\vlb}{\mathbf{lb}}
\newcommand{\vub}{\mathbf{ub}}

% sets as caligraphics
\newcommand{\cV}{\mathcal{V}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cO}{\mathcal{O}}

@@

%%%%%%%%%%%%%
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}

@@

We propose robust motion execution as a framework that take pre-planned trajectories as input and compensate for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
Consider the example in Fig.~\ref{fig:swap2:initial}, where two robots are tasked with swapping their position.
The pre-planned trajectories are collision-free, but neither consider a new obstacle nor that the blue robot does not start it the right location.
Robust motion execution can be used to still successfully swap positions, while staying as close as possible to to the pre-planned trajectories (see Fig.~\ref{fig:swap2:final}).
Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and obstacles around them.

\begin{figure}
\centering
\subfloat[Initial configuration.]{
\includegraphics[width=0.48\textwidth]{images/swap2_initial.pdf}
\label{fig:swap2:initial}
}
\hfill
\subfloat[Final configuration and executed trajectories.]{
\includegraphics[width=0.48\textwidth]{images/swap2_final.pdf}
\label{fig:swap2:final}
}
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
%\caption{Initial configuration.}
%\label{fig:swap2:initial}
%\end{subfigure} \hfill
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
%\caption{Final configuration and executed trajectories.}
%\label{fig:swap2:final}
%\end{subfigure}
\caption{Two robots (green and blue circles) are tasked with following their preplanned trajectories (green and blue dashed lines).
The initial plans were created without knowledge of the obstacle (gray) and the blue robot does not start at its planned start position.
Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the preplanned trajectory.
}
\label{fig:swap2}
\end{figure}

Robust motion execution is an extension of cooperative collision avoidance where our objective is to stay close to the originally planned trajectories as much as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with dynamic receding horizon.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.

\todo{perhaps write some more about what experiments we did, after we have the material}

\section{Problem Formulation} \label{problemFormulation}
% assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
% input: original curves; positions of peers; dynamic limits; environment (at least able to sense); dt; curve_count; T
% output: at each dt: new trajectory such that there is no collision (guaranteed)
% issues: no live-lock guarantee

We consider a group of $m$ robots and each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory of $i^{th}$ robot where } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R_i(\vp)&:\text{ physical extend of robot $i$ at position $\vp$}, and\\
    \gamma_j&: \text{ dynamic limit of robots for $j^{th}$ derivation degree}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
\end{align*}

At time $t$ each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
However, robots cannot communicate with each other and are unaware of the other robots' trajectories.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ needs to execute a trajectory $\vf_i(t)$ such that:
\begin{align*}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i(0)}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision free, and}\\ 
    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j,\\
    \text{where } & t\in [0,T_i].
\end{align*}

We approximately solve this problem using a dynamic receding horizon approach.
At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position.
We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.

%\todo{add paragraph about how we actually (approximately solve this problem)}

% \begin{align*}
%     \text{Given,}\ \ \ \ \ &\\
%     \vo^i(t')&:\text{ original trajectory of robot $i$},\\
%     ct&:\text{ current global time},\\
%     \delta t&:\text{ replanning period},\\
%     \tau&: \text{time horizon},\\ 
%     c&:\text{ maximum continuity between pieces},\\
%     \cO&:\text{ free space representation of the environment},\\
%     \{\vp_i\}&:\text{ set of positions of all robots},\\
%     \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
%     &\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
%     \text{find a new}&\text{ trajectory $\vf^{i,K}(t)$ such that},\\
%     \vf^{i,K}(t)&\text{ is}\text{ continuous up to degree $c$ for }t\in [0,\tau],\\
%     \frac{d^j\vf^{i,K}}{dt^j}(0) &= \frac{d^j\vf^{i,K-1}}{dt^j}(\delta t)\text{ for } j\in\{0,1,...,c\}\\
%     \vf^{i,K}(t)&\text{ is collision free for $t\in [0,\delta t]$},\\
%     \vf^{i,K}(t)&\text{ tracks $\vo^i(t')$ as close as possible for $t\in[0,\tau]$ or equivalently $t'\in[ct, ct+\tau]$ }, \text{and}\\
%     \left\|\frac{d^j \vf^{i,K}(t)}{dt^j}\right\| &\leq \gamma_j\text{ for } t\in [0,\tau],\\
% \end{align*}

@@

\subsection{Buffered Voronoi Cells} \label{bufferedVoronoi}
Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
\begin{align}
    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_i\leq 0 \right\} \label{voronoi_cell_definition}
\end{align}
where $\|\vp\|$ is the L2-norm of vector $\vp$.

The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ that is bounded by hyperplane $H_i^j$ that separates point $\vp_i$ from $\vp_j$ with normal $\valpha_i^j$ and distance along normal $\beta_i^j$ where $\valpha_i^j\in \R^n$ and $\beta_i^j\in \R$ such that
\begin{align}
    \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
    \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i. \label{voronoiBeta}
\end{align}

@@

The hyperspace $\cS_i^j$ has the following definition:
\begin{align}
    \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}
\end{align}

Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
\begin{align}
    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
\end{align}

Thus, we can compute the buffered voronoi cell of any robot $i$ as the set of hyperplanes $H_i^j$ in $O(m)$ time.

\subsection{B\'ezier Curves} \label{bezierCurves}
A degree $d$ B\'ezier curve $\vf(t)$ parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
\begin{align}
    \vf(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T
\end{align}

The curve starts at $\vP_0$ and ends at $\vP_d$. It does not interpolate the control points, but uses them to guide the curve. A B\'ezier curve lies completely inside the convex hull of its control points \cite{Bernstein}. This is called the \emph{convex hull property of B\'ezier curves}. We use this property to give robot-to-robot and robot-to-obstacle no-collision guarantees.

We use splines as trajectories where each piece is a B\'ezier curve. Given a trajectory $\vf^{K}_i(t)$ for robot $i$ at time step $K$ with $l$ pieces and duration $T^{K}_i$, $T^{K}_{i,j}$ denotes the duration of $j^{th}$ piece, $\vf^{K}_{i,j}(t; T^{K}_{i,j})$ denotes the $j^{th}$ piece of the trajectory, $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of $j^{th}$ piece, and $P^{K}_{i,j,\rho}[u]$ denotes the $u^{th}$ coordinate of that control point where $j \in \{1,2,...,l\}$, $\rho \in \{0,1,...,d\}$, and $u \in \{1,2,...,n\}$.

\subsection{Support Vector Machine}\label{svmSection}
A support vector machine is a supervised learning method that is used to classify data into several classes.
In binary classification problems, we are given a linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label.
The goal is to find a hyperplane with normal $\vw$ and distance along the normal $\frac{b}{\|w\|}$ that separates the two classes.
The SVM problem for binary classification with a separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
\begin{align*}
    \text{minimize}\ \ \  &\|\vw\|\\
    \text{subject to}\ \ \  & y_i(\vw \cdot \vx_i - b) \geq 1
\end{align*}
We use SVMs to define collision free convex subspaces that are obstacle-free.
\subsection{Trajectory Optimization} \label{trajectoryOptimization}
A part of our replanning approach utilizes quadratic programming for trajectory optimization using control points of curves as decision variables. The overall structure of our quadratic optimization problem is as follows:
\begin{align*}
    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^T\vg\\
    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA
    % &\vlb \leq \vx \leq \vub
\end{align*}
%, while bounds on variables are represented with vectors the $\vlb$ and the $\vub$.

A quadratic cost function is represented using the matrix $H$ and the vector $\vg$. The constraints are represented using the matrix $A$ with vectors $\vlbA$ and $\vubA$.
Notice that all constraints should be linear in the decision variables.

There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.

\begin{description}
\item [Initial Point Constraints]
An initial point constraint on a B\'ezier curve requires the first control point of the curve to be equal to a given vector. This requires $n$ linear constraints on the control points, $n$ being the dimension we are working in.

\item[Continuity Constraints]
A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ in the end to be equal to the curve $j+1$ in the beginning in any order of derivation. We take the vector difference of those values and require it to be equal to $\vzero$. This requires $n$ linear constraints on the control points.

\item[Hyperspace Constraints]
A hyperspace constraint requires a point of a curve to be on a specific side of a hyperplane. Given a hyperplane with normal $\vn$ and distance along the normal $b$, the hyperspace constraint requires $1$ linear constraint on the control points.
\end{description}

\section{Approach}

@@

\subsection{Approach Overview}
Our approach has three major components: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot.

In each iteration $K$, each robot executes the flow chart outlined in Fig. ~\ref{fig:flowchart}. Replanning is done at a fixed period of $\delta t$ and results in a trajectory $f^K_i(t)$ that is defined for $t\in [0,\tau]$, safe to execute up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.

In the beginning of each iteration, we check several conditions to decide if discrete planning is required. If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth. We use this discrete path as an initial guess in trajectory optimization. If discrete planning is not required, we skip discrete search, and directly use the control points of the previous plan as the initial variables.

Depending on whether discrete search is done or not, we construct the objective matrix $H$ and objective vector $g$ for trajectory optimization in a slightly different way. Exact difference in construction processes is explained in ~\ref{continuousOptimization}.

Than, we compute the $A$ matrix that represents continuity, hyperspace, and initial point constraints. Robot-to-robot collision avoidance is enforced with buffered voronoi decomposition of the space while robot-to-obstacle collision avoidance is enforced with SVM hyperspaces that we calculate between trajectory pieces and the obstacles. Since quadratic optimization requires constraints to be linear and dynamic limits can't be represented as linear constraints, we check dynamic limit violations not during trajectory optimization but in the temporal rescaling stage that runs after optimization. As long as dynamic limits are violated, we increase durations of pieces and do the optimization again until dynamic limits are not violated. In the end, we have a trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is $C^{(c)}$ continuous, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.

\begin{figure}
%\begin{adjustbox}{width=\textwidth,caption={bla}}
\resizebox{\textwidth}{!}{
% \footnotesize
\begin{tikzpicture}[node distance = 2cm]
    \node (discrete) [decision, text width=2cm] {need discrete replanning?};
    \node (discretesearch) [process, right of=discrete, xshift=1.2cm, yshift = 1cm, text width = 2cm] {discrete search};
    \node (discobjbuild) [process, right of=discretesearch, xshift = 1cm, text width = 2cm] {discrete objective builder};
    \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {continuous objective builder};
    \node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
    {constraint builder};
    \node (trajopt) [process, right of=constraintbuild, xshift = 1cm, text width = 2cm] {trajectory optimization};
    \node (dynamiclimits) [decision, right of=trajopt, xshift = 1.5cm, text width = 2cm] {dynamic limits violated?};
    \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {rescaling};
    %\node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};

    \coordinate[above=2cm of discrete.west, xshift=-0.2cm, yshift=0.2cm] (c1);
    \coordinate[below=2cm of discrete.west, xshift=-0.2cm, yshift=-0.2cm] (c2);
    \coordinate[above=2cm of discretesearch.east, xshift = 0.2cm, yshift=-0.8cm] (c3);
    \coordinate[below=2cm of discretesearch.east, xshift = 0.2cm, yshift = -1.2cm] (c4);

    \coordinate[above=2cm of discobjbuild.west, xshift=-0.2cm, yshift=-0.8cm] (c5);
    \coordinate[below=2cm of discobjbuild.west, xshift=-0.2cm, yshift = -1.2cm] (c6);
    \coordinate[above=2cm of trajopt.east, xshift = 0.2cm] (c7);
    \coordinate[below=2cm of trajopt.east, xshift = 0.2cm, yshift=-0.4cm] (c8);
